---
title: "Analytic Code"
date: "Last updated `r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
---

```{r, include = F}
knitr::opts_chunk$set(message = F, warning = F)
```


# Load data and packages

```{r, message = F, warning = F}
library(here) # for engaging with working environment
library(rio) # for importing excel files
library(psych) # for scoring multiple choice items
library(R.utils) # just for the insert() function
library(conflicted)
library(tidyverse) # for data cleaning and manipulation
conflict_prefer("here", "here")
conflict_prefer("filter", "dplyr")
conflict_prefer("count", "dplyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("summarise", "dplyr")
```

## Qualtrics survey responses

The excel files contain raw data exported from Qualtrics. The first row of this file contains variable names, but rows 2 and 3 contain meta data. To account, we first load in all data as a "names" data frame and then data starting at row 4, for the raw data. 

```{r, message = F, warning = F, eval = F}
# read in form A (Prolific)
formA_names = read_csv(
  here("data/Form+A_Prolific_April+2,+2021_15.27.csv"))

formA = read_csv(
  here("data/Form+A_Prolific_April+2,+2021_15.27.csv"), 
  col_names = F, skip = 3)

names(formA) = names(formA_names)
rm(formA_names)

# read in form A (MTurk)
formA_names = read_csv(
  here("data/Form A_April 2, 2021_15.41.numeric.csv"))

formA2 = read_csv(
  here("data/Form A_April 2, 2021_15.41.numeric.csv"), 
  col_names = F, skip = 3)

names(formA2) = names(formA_names)
rm(formA_names)

formA = full_join(formA, formA2)
rm(formA2)

# read in form B (Prolific)
formB_names = read_csv(
  here("data/Form+B_Prolific_April+2,+2021_15.27.csv"))

formB = read_csv(
  here("data/Form+B_Prolific_April+2,+2021_15.27.csv"), 
  col_names = F, skip = 3)

names(formB) = names(formB_names)
rm(formB_names)


# read in form B (MTurk)
formB_names = read_csv(
  here("data/Form B_April 2, 2021_15.44.numeric.csv"))

formB2 = read_csv(
  here("data/Form B_April 2, 2021_15.44.numeric.csv"), 
  col_names = F, skip = 3)

names(formB2) = names(formB_names)
rm(formB_names)

formB = full_join(formB, formB2)
rm(formB2)

# read in form C (Prolific)
formC_names = read_csv(
  here("data/Form+C_April+16,+2021_17.21.csv"))

formC = read_csv(
  here("data/Form+C_April+16,+2021_17.21.csv"), 
  col_names = F, skip = 3)

names(formC) = names(formC_names)
rm(formC_names)
```

```{r, eval = F, echo = F}
save(formA, formB, formC, file = here("data/raw_data.Rdata"))
```

```{r, echo = F}
load(here("data/raw_data.Rdata"))
```

In forms A and B, variable names composed solely of numbers (e.g., 20001) refer to the specific variable number as included in the dictionary. These must be prefaced by `q_` for readability. 

```{r}
names(formA) = str_replace(names(formA), # look in this vector of strings
                           "(^)([0-9]*$)", #match two parts. part 1: beginning of string, second part: digits 0 or more times and then the string ends
                           "q_\\2") # replace with q_ followed by the second part of the match

names(formB) = str_replace(names(formB), 
                           "(^)([0-9]*$)", 
                           "q_\\2") 

names(formC) = str_replace(names(formC), 
                           "^Q", 
                           "q_") 

# an additional error in form C -- some variable names were coded with only the last 4 digits (i.e., missing the first "2")
names(formC) = str_replace(names(formC), 
                           "(q_)(\\d{4}$)", "\\12\\2")
```

Remove participants without valid Prolific or MTurk IDs.

```{r}
formA = formA %>%
  dplyr::filter(!is.na(mTurkCode) | str_length(PROLIFIC_PID) > 3)
formB = formB %>%
  dplyr::filter(!is.na(mTurkCode) | str_length(PROLIFIC_PID) > 3)
formC = formC %>%
  dplyr::filter(str_length(PROLIFIC_PID) > 3)
```

## Scoring keys

```{r, message = F, warning = F}
keyA = read.csv(here("keys/key_A.csv"))
keyB = read.csv(here("keys/key_B.csv"))
keyC = import(here("keys/key_C.xlsx"), sheet = 1)
```

Variable names composed solely of numbers (e.g., 1) refer to the response choice number as presented to participants. These must be prefaced by `R_` for readability. 

```{r}
names(keyA) = str_replace(names(keyA), 
                           "(^X)([0-9]{1}$)", 
                           "R_\\2") 

names(keyB) = str_replace(names(keyB), 
                           "(^X)([0-9]{1}$)", 
                           "R_\\2") 

names(keyC) = str_replace(names(keyC), 
                           "(^)([0-9]{1}$)", 
                           "R_\\2") 
keyC = dplyr::rename(keyC, X = .)
```

The `Key` column indicates the position of the correct response. We create a key vector that contains the value of the correct response, not the position.

```{r}

create_key = function(keydf){
  # select only response variables and concatonate by row into vectors
  keydf$response_vector = keydf %>%
    select(starts_with("R")) %>%
    pmap(~c(..1, ..2, ..3, ..4, ..5, ..6))

  # map across response vectors and key positions to pull out correct answer
  keydf = keydf %>%
    mutate(answer = map2_chr(response_vector, Key,
                         ~.x[.y]))
  return(keydf)
}

keyA = create_key(keyA) %>%
  mutate(form = "A")
keyB = create_key(keyB) %>%
  mutate(form = "B")
keyC = create_key(keyC) %>%
  group_by(Stimulus) %>%
  dplyr::mutate(form = ifelse(dplyr::row_number() == 1, "C", "D")) %>%
  ungroup()
```

Merge keys together.

```{r}
masterKey = keyA %>%
  full_join(keyB) %>%
  full_join(keyC) %>%
  select(X:Key, answer, form) %>%
  dplyr::rename(item = X)
```


# Score data new

First, we merge all raw datasets.

```{r}
all_data = formA %>%
  full_join(formB) %>%
  full_join(formC)
```

```{r}
alldata_scored = score.multiple.choice(
  key = masterKey$Key, 
  data = all_data[, masterKey$item], 
  score = FALSE)
```

Remove items which were mistakes (see key_C, sheet entitled linking C to A and B.)

```{r, eval = T}
remove_items = c(
    "q_21148",
    "q_22573",
    "q_22496",
    "q_20052",
    "q_21409",
    "q_22068",
    "q_22169",
    "q_21911",
    "q_21185",
    "q_21288",
    "q_20790",
    "q_20033",
    "q_24285",
    "q_23402",
    "q_24824",
    "q_23044",
    "q_25399",
    "q_23847",
    "q_23990",
    "q_23485",
    "q_24709",
    "q_23602",
    "q_24676",
    "q_25281",
    "q_23456",
    "q_20479",
    "q_23832")

remove_which = which(masterKey$item %in% remove_items)

alldata_scored = alldata_scored[, -remove_which]
masterKey = dplyr::filter(masterKey, !(item %in% remove_items))
all_data = select(all_data, -all_of(remove_items))
```

# Data for publication

## Demographics

```{r}
demo = all_data %>%
  mutate(comb_id = case_when(
    !is.na(prolificID) ~ prolificID,
    !is.na(mTurkCode) ~ as.character(mTurkCode),
    TRUE ~ NA_character_)) %>%
  mutate(source = case_when(
    !is.na(prolificID) ~ "Prolific",
    !is.na(mTurkCode) ~ "MTurk",
    TRUE ~ NA_character_)) %>%
  dplyr::mutate(row = row_number() + 1000) %>%
  group_by(comb_id) %>%
  dplyr::mutate(row = min(row)) %>%
  dplyr::mutate(PID = paste0("R", row)) %>%
  ungroup() %>%
  dplyr::rename(duration = `Duration (in seconds)`) %>%
  dplyr::mutate(
    english_cat = case_when(
      english == 1 ~ "Very well (fluent/native)",
      english == 2 ~ "Well",
      english == 3 ~ "Not well",
      english == 4 ~ "Not at all (Need translation)",
      TRUE ~ NA_character_),
    growup_cat = case_when(
      growup == 1 ~ "United States of America",
      growup == 2 ~ "Outside of the US"),
    live_cat = case_when(
      live == 1 ~ "Yes",
      live == 2 ~ "No"),
    state = recode(states, 
                    !!!c(state.name[1:50], "District of Columbia")
                    ),
    sex = case_when(
      sex == 1 ~ "Male",
      sex == 2 ~ "Female",
      sex == 3 ~ "Other",
      sex == 4 ~ "Prefer not to say"),
    edu = case_when(
      edu == 0 ~ "Less than 12 years", 
      edu == 1 ~  "High school grad/GED",
      edu == 2 ~  "Currently in college/university",
      edu == 3 ~  "Some college/university, but did not graduate",
      edu == 4 ~  "Associate degree (2 yr)",
      edu == 5 ~  "College/university degree (4 yr)",
      edu == 6 ~  "Currently in grad/professional school",
      edu == 7 ~  "Grad/professional degree"),
    ethnic = case_when(
     ethnic == 1 ~ "American Indian/Alaskan Native",
     ethnic == 2 ~ "Asian",
     ethnic == 3 ~ "Black",
     ethnic == 4 ~ "Hispanic",
     ethnic == 5 ~ "White",
     ethnic == 6 ~ "Mixed (two or more)",
     ethnic == 7 ~ "Other"),
    hhinc = case_when(
      hhinc == 1 ~ "< 20K",
      hhinc == 2 ~ "20K-40K",
      hhinc == 3 ~ "40K-60K",
      hhinc == 4 ~ "60K-80K",
      hhinc == 5 ~ "80K-100K",
      hhinc == 6 ~ "100K-120K",
      hhinc == 7 ~ "120K-150K",
      hhinc == 8 ~ "150K-200K",
      hhinc == 9 ~ "200K-250K",
      hhinc == 10 ~ "250K-350K",
      hhinc == 11 ~ "350K-500K",
      hhinc == 12 ~ "> 500K",
      hhinc == 13 ~ "Prefer not to say"))
```

Participants are excluded from analyses if they
* complete the survey in less than 3 minutes (180 seconds),
* don't speak fluent English,
* grew up outside the US, or
* are currently living outside the US.

```{r}
demo = demo %>%
  mutate(included = case_when(
    duration < 180 ~ "No",
    english > 2 ~ "No",
    growup == 2 ~ "No",
    live == 2 ~ "No",
    TRUE ~ "Yes"
  ))
```

163 rows are excluded on this basis.

```{r}
demo = demo %>%
  select(PID, source, StartDate, duration, english_cat, growup_cat, live_cat, state, age, sex, edu, ethnic, hhinc, included)

names(demo) = str_remove(names(demo), "_cat")

demo$prop_correct <- alldata_scored %>% rowMeans(na.rm = T)

```


```{r}
alldata_scored_df = as.data.frame(alldata_scored)
data_scored = cbind(demo, alldata_scored)
write_csv(data_scored, 
          file = here("data/TDA_data_scored.csv"))

# This output file has been posted on Dataverse at
# https://doi.org/10.7910/DVN/5T80PF
```


We also save a shortened version of the master key object.

```{r}
masterKey %>%
  select(item, answer, form) %>%
  dplyr::rename(adjective = answer) %>%
  write_csv(file = here("data/masterkey.csv"))

# This output file has been posted on Dataverse at
# https://doi.org/10.7910/DVN/5T80PF
```




